Designing and modeling a browser-based distributed evolutionary computation systems

### 2015-04-01 modeling-volunteer-computing-gecco.tex
Finishing description

When the experiment is finished, that is, the solution has been found,
the server is restarted using  command line tools provided by
Heroku. Every experiment was first done during the talk and then
announced in Twitter several times until enough data was gathered.

As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in the GitHub
repository \url{https://github.com/JJ/idc-keynote}. %FERGU: JJ, es
                                %este el repo correcto, no?
% Todo esto lo voy a cambiar, no lo mires mucho m·s que por
% metodologÌa. Ahora uso http://github.com/JJ/splash-volunteer
These results
will be analyzed in the next section.

>>>>

During and after the experiment, the data can be collected from one of
the logs: the log file (if the PaaS allows writing to the filesystem,
which is not the case in Heroku) or to online logging services such as
Loggly, which is the one we are using.

As indicated in the introduction, every part of the experiment and
data gathered have been released as free software in the GitHub
repository \url{https://github.com/JJ/splash-volunteer}. 
will be analyzed in the next section.
